Verifying Demonstrations

### 2020-02-26 paper/DBSchnorr-n-bit.tex
Fixes missing } for a \cref

The prover must know the responses for both challenges to successfully pass the \ac{DB} phase.
The reason for the two challenges but only one random nonce is that knowing the responses to both means learning \(\alpha\).
This allows us to prevent \ac{DBTF}.
Bundling the authentication into the distance-bounding phase (difference from Brands-Chaum) prevents \ac{DBDH}, and both adaptations together aim at \ac{DBMF} resistance. %reducing success of MF according to number of repetitions.
The reason we use secret sharing and not \(s_b\) directly, is to bound the \(l\) bits the verifier must learn of \(s_{1-b}\).
Without secret sharing, the verifier learns \(l\) bits of \(s_{1-b}\), but with secret sharing the verifier learns \(l\) bits of \emph{one share}.
Thus, we still have information theoretic security for \(s_{1-b}\)
although we reveal the \(l\) bits. (See \cref{l-bit-problem for an
  in-depth treatment of what we call the \(l\)-bit problem.)

@@

The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that we made. 
It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.

>>>>

The prover must know the responses for both challenges to successfully pass the \ac{DB} phase.
The reason for the two challenges but only one random nonce is that knowing the responses to both means learning \(\alpha\).
This allows us to prevent \ac{DBTF}.
Bundling the authentication into the distance-bounding phase (difference from Brands-Chaum) prevents \ac{DBDH}, and both adaptations together aim at \ac{DBMF} resistance. %reducing success of MF according to number of repetitions.
The reason we use secret sharing and not \(s_b\) directly, is to bound the \(l\) bits the verifier must learn of \(s_{1-b}\).
Without secret sharing, the verifier learns \(l\) bits of \(s_{1-b}\), but with secret sharing the verifier learns \(l\) bits of \emph{one share}.
Thus, we still have information theoretic security for \(s_{1-b}\)
although we reveal the \(l\) bits. (See \cref{l-bit-problem} for an
  in-depth treatment of what we call the \(l\)-bit problem.)

@@

The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices we made. 
It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.

### 2020-02-26 paper/distance-bounding.tex
Fixes typos in DH definition

The intuition is that an adversary (malicious, far-away prover) must commit to 
an action: either respond with an own message, which is determined before 
seeing the challenge, or to prompt a nearby prover to respond (with a message 
chosen by the adversary).
Technically, this adversary can do more than \iac{DBDH} adversary normally can.
\Textcite{TREAD} captured this by two dummy sessions \(\sid_{\Commit}\) and 
\(\sid_{\Prompt}\).
The adverary commits to his action by \enquote{sending} \((\sid, k+1, 
m'_{k+1})\) in dummy session \(\sid_{\Commit}\).
If \(m'_{k+1} = \Prompt\), then he must also \enquote{send} a message in dummy 
session \(\sid_{\Prompt}\), which is the message the nearby prover will send.

\begin{definition}[Tainted session, \acs*{DBDH}~\cite{TREAD}]%
  \label{TaintedDH}
  A time-critical round \(\Xscript{\sid}{k, k+1} = (m_k, m_{k+1})\), for some 
  \(k\geq 1\) and \(m_k\) send by the verifier, of an adversary--verifier 
  session \(\sid\) is \emph{tainted} if one of the following conditions holds.
  \begin{itemize}
    \item The maximal \(j\) with \(\Xscript{\sid_{\Commit}}{j} = (\sid, k+1, 
      m_{k+1}')\) for \(m_{k+1}' \neq \Prompt\) and \(\marker{\sid, k} > 
      \marker{\sid_{\Commit}, j}\) satisfies \(m_{k+1}' \neq m_{k+1}\) (or no 
      such \(j\) exists).

>>>>

The intuition is that an adversary (malicious, far-away prover) must commit to 
an action: either respond with an own message, which is determined before 
seeing the challenge, or to prompt a nearby prover to respond (with a message 
chosen by the adversary).
Technically, this adversary can do more than \iac{DBDH} adversary normally can.
\Textcite{TREAD} captured this by two dummy sessions \(\sid_{\Commit}\) and 
\(\sid_{\Prompt}\).
The adverary commits to his action by \enquote{sending} \((\sid, k+1, 
m'_{k+1})\) in dummy session \(\sid_{\Commit}\) before receiving the challenge 
in message \(k\) in session \(\sid\) (making message \(k+1\) in \(\sid\) his 
response to the challenge).
If \(m'_{k+1} = \Prompt\), then he must also \enquote{send} a message in dummy 
session \(\sid_{\Prompt}\), which is the message the nearby prover will send.

\begin{definition}[Tainted session, \acs*{DBDH}~\cite{TREAD}]%
  \label{TaintedDH}
  A time-critical round \(\Xscript{\sid}{k, k+1} = (m_k, m_{k+1})\), for some 
  \(k\geq 1\) and \(m_k\) send by the verifier, of an adversary--verifier 
  session \(\sid\) is \emph{tainted} if one of the following conditions holds.
  \begin{itemize}
    \item The maximal \(j\) with \(\Xscript{\sid_{\Commit}}{j} = (\sid, k+1, 
      m_{k+1}')\) for \(m_{k+1}' \neq \Prompt\) and \(\marker[\sid, k] > 
      \marker[\sid_{\Commit}, j]\) satisfies \(m_{k+1}' \neq m_{k+1}\) (or no 
      such \(j\) exists).
